Z-Resonance at LEP

### 2010-08-03 Z0-Publikation/tex/paper-template.tex
fit als bild besser

These cross sections have then been used as data for a fit. By fitting the data
points the overall hadronic cross section $σ_0^{\mathrm{had}}$, the mass $m_Z$ and the decay width $Γ_Z$
of the $Z^0$-boson could be determined. The results can be found in
\tref{results}.

@@

Starting from these values and already knowing the decay width of the $Z^0$-boson as well as its mass, we can again do a fit on these three data points. This time the only free parameter is the muonic cross section $σ_0^μ$.

@@

\begin{figure}[htb]
 \centering
 \includegraphics[width=1\columnwidth,keepaspectratio]{finalhad_fit}
 \caption{Breit-Wigner-Fit hadrons}
 \label{fig:e_vis}
\end{figure}

\begin{figure}[htb]
 \centering
 \includegraphics[width=1\columnwidth,keepaspectratio]{finalmu_fit}
 \caption{Breit-Wigner-Fit muons}
 \label{fig:n_cluster}
\end{figure}

>>>>

These cross sections have then been used as data for a fit (see
\fref{fit_hadrons}). By fitting the data
points the overall hadronic cross section $σ_0^{\mathrm{had}}$, the mass $m_Z$ and the decay width $Γ_Z$
of the $Z^0$-boson could be determined. The results can be found in
\tref{results}.

\begin{figure}[htb]
 \centering
 \includegraphics[width=1\columnwidth,keepaspectratio]{finalhad_fit}
 \caption{Breit-Wigner-fit for hadronic events}
 \label{fig:fit_hadrons}
\end{figure}

@@

Starting from these values and already knowing the decay width of the
$Z^0$-boson as well as its mass, we can again do a fit on these three data
points (see \fref{fit_muons}). This time the only free parameter is the muonic
cross section $σ_0^μ$.

\begin{figure}[htb]
 \centering
 \includegraphics[width=1\columnwidth,keepaspectratio]{finalmu_fit}
 \caption{Breit-Wigner-fit for muonic events}
 \label{fig:fit_muons}
\end{figure}

@@
